### 2015-07-07 narrative/proposed-work.tex
edits for 1.3

\underline{Principle 1:} {\bf A knowledge-centric system design}, let user knowledge  to
define data policies. Today Storage System and I/O layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layer in a highly integrated fashion where user
will place their intentions into the system and actions will dynamically and
statically take place to optimize for both the system and for individual
requests.

>>>>

\underline{Principle 1:} {\bf A knowledge-centric system design} that allows user knowledge  to
define data policies. Today Storage System and I/O layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layer in a highly integrated fashion where users
will place their intentions into the system and actions will statically and dynamically
take place to optimize for both the system and for individual
requests.
